Git Learning Notes

### 2014-01-30 ch-wox/ch-wox.tex
nawox initial

We have investigated the growth dynamics of each source in OT configuration. In each experiments, we control the temperature, flow rate and source and substrate locations. Another parameter we found important is the growth number\footnote{Defined as the order of growth performed in the same reaction chamber} in the same reaction chamber. Usually one will conduct several runs in the same chamber, and different results may arise with respect to the growth number. With this degree of freedom included, we first summarized the primary features of deposition and the associated parameters in Table~\ref{tab:wot}.
% \ce{WO_x} ordinary transport results
\begin{table}[htb]
\centering
\caption{\ce{WO_x} ordinary transport results}\label{tab:wot}
\begin{tabular}{lp{2in}p{2in}r}
\toprule
\multicolumn{2}{c}{Growth Number} \\
\cmidrule(l){2-3}
 Source   & First & Second and more & Sodium(ppm)   \\
\midrule
3N      & Morphology from high to low temperature: islands, dense layer and a few NWs & Dense wires become more and more, \ce{NaxWO3} phase dominates & 20  \\
3N5     & $\pm1$  & correlated to flow &      NA\\
4N5  & dense islands, some tiny wires in low temperature end & NA & 0.065 \\
5N  & dense islands, some tiny wires in low temperature end  & NA & 0.05\\
\bottomrule
\end{tabular}
\end{table}

@@

Before diving into the complex interaction of \ce{WO3} and \ce{Na_xWO3} nanostructures, we would like to examine the metallic W source itself and its changes after growth. The SEM images of all powders before and  after growth are shown in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
% powder before growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{pd_before.jpg}
\caption[SEM images of W powder before growth]{SEM images of W powder before growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
\label{fig:pdbefore}
\end{figure}

% powder after growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{pd_after.jpg}
\caption[SEM images of W powder after growth]{SEM images of W powder after growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
\label{fig:pdafter}
\end{figure}

Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate was shown in Fig.~\ref{fig:nawoxsemedx}(a). The nanostructures are NWs with lengths from tens microns up to several hundred microns and diameters about 40 to 500 nm. The deposition of nanowires was generally located on the substrates with a growth temperature range from 660 to 420 \si{\degreeCelsius}. Close-up observations at high magnification revealed some nanowires were cylinder-shaped and some were belt-shaped. At some locations, microplate structures with a regular rectangular shape grew among the nanowires as demonstrated in Fig.~\ref{fig:nawoxsemedx}(b) and its inset. The chemical compositions of the deposition were identified by EDX. A representative EDX spectrum in Fig.~\ref{fig:nawoxsemedx}(c) shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate. The crystal structures of the as-synthesized specimens were examined using XRD. The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}(d). The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase\footnote{ICDD PDF 04-012-4449,\emph{a}=7.2740\AA, \emph{b}=7.2911\AA, \emph{c}=18.5510\AA, $\alpha$=96.3750$^\circ$, $\beta$=90.8920$^\circ$, $\gamma$=119.6560$^\circ$} and the triclinic \ce{Na2W4O_{13}} phase.\footnote{ICDD PDF 04-012-7108,\emph{a}=11.1630\AA, \emph{b}=3.8940\AA, \emph{c}=8.2550\AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$} The tungsten oxide is the monoclinic \ce{WO3} phase.\footnote{ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA, $\beta$=90.8920$^\circ$}

@@

The XRD measurements revealed the overall structure of the depositions on the substrates. To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and EDX were performed on more than 20 nanowires. The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase. (Fig.~\ref{fig:nawoxtem}(a-c)) The HRTEM image in Fig.~\ref{fig:nawoxtem}(b) reveals that the nanowire has a single-crystalline structure. The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}(b) was recorded in $[\bar{1}10]$ axis. Based on the analyses on a series of diffraction patterns and HRTEM images, the nanowire was confirmed as the triclinic \ce{Na5W_{14}O_{44}}. The growth direction of \ce{Na5W_{14}O_{44}} NWs was determined to be parallel to the (001) plane. The chemical composition of the nanowire was revealed by EDX. Fig.~\ref{fig:nawoxtem}(c) shows the nanowire consisted of W, Na, and O. No other impurities were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder. They are not compositions from the nanowires and other structures studied here.} small fraction of nanowires were found to be the monoclinic \ce{WO3} phase. (Fig.~\ref{fig:nawoxtem}(d-f)) The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}(e) was recorded in [100] zone.

@@

Using 3N source and with increasing growth number from 1 to 5, we found dramatic morphology variation of as-synthesized nanostructures. The typical morphologies evolution as to the growth numbers is illustrated in Fig.~\ref{fig:nawoxsemall}.

@@

The sodium concentration was 20ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.}
% 3N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
\label{fig:wox3n5}
\end{figure}

% 4N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox4n5.jpg}
\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
\label{fig:wox4n5}
\end{figure}

@@

Commercial available tungsten powders with different size are usually associated with purity variation as well. We investigated four kinds of tungsten powder as already summarized in Table~\ref{tab:powder}. The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.

We performed a systematic investigation on the oxidation behavior of tungsten powder. In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 5--8 mTorr. Then oxygen flow varying between 1 sccm to 10 sccm was admitted from upstream inlet. With 10 sccm Ar as carrier gas, the overall pressure was about 100 mTorr. The heating temperature was in the range of 500 to 750 \si{\degreeCelsius}. We present the temperature effect, size-dependence and influence of oxygen partial pressure as following.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{JAP-2column_Fig1.jpg}
\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500\si{\degreeCelsius}, b) 600\si{\degreeCelsius}, c) 650\si{\degreeCelsius}, d) 750\si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650\si{\degreeCelsius}. Oxygen flow rate is 1 sccm.}
\label{fig:pdtemp}
\end{figure}

Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder. At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow. When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface. Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures. It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{JAP-2column_Fig3.jpg}
\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow. a) $17\mu m$, b) $32\mu m$, c) $3.3\mu m$, d) $1.5\mu m$.}
\label{fig:pdsize}
\end{figure}

Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions. In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature. This dramatic difference could be explained in terms of surface energy and oxygen diffusion. With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder. When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition. Since the size distribution of 3N powder is more uniform than that of 3N5 powder, we only employed the former as seeds.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{JAP-2column_Fig2.jpg}
\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm. The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
\label{fig:pdoxy}
\end{figure}

@@

%FG

% fg sem 
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:sg1}\includegraphics[width=0.45\textwidth]{wox_flow1}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:sg2}\includegraphics[width=0.45\textwidth]{wox_flow2}}
\caption[Characterization of flow growth \ce{WO3}: SEM]{ (a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
\label{fig:fgsem}
\end{figure}

% fg tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{wo3_tem.jpg}
\caption[Flow growth of \ce{wo3}:TEM]{TEM characterization of FG \ce{WO3} NWs. }
\label{fig:fgtem}
\end{figure}

>>>>

We have investigated the growth dynamics of each source in OT configuration. In each experiments, we control the temperature, flow rate and source and substrate locations. Another parameter we found important is the growth number\footnote{Defined as the order of growth performed in the same reaction chamber} in the same reaction chamber. Usually one will conduct several runs in the same chamber, and different results may arise with respect to the growth number. With this degree of freedom included, we first summarized the primary features of deposition and the associated parameters in Table~\ref{tab:wot}.
% \ce{WO_x} ordinary transport results
\begin{table}[htb]
\centering
\caption{\ce{WO_x} ordinary transport results}\label{tab:wot}
\begin{tabular}{lp{2in}p{2in}r}
\toprule
\multicolumn{2}{c}{Growth Number} \\
\cmidrule(l){2-3}
 Source   & First & Second and more & Sodium(ppm)   \\
\midrule
3N      & Morphology from high to low temperature: islands, dense layer and a few NWs & Dense wires become more and more, \ce{NaxWO3} phase dominates & 20  \\
3N5     & islands in high temperature end and layers in low temperature end & NA &      NA\\
4N5  & dense islands, some tiny wires in low temperature end & NA & 0.065 \\
5N  & similar to those of 4N5  & NA & 0.05\\
\bottomrule
\end{tabular}
\end{table}

@@

Before diving into the growth of \ce{WO3} and \ce{Na_xWO3} nanostructures using 3N powders, we would like to examine the metallic W source itself and its changes after growth. The SEM images of all powders before and  after growth are shown in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
% powder before growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{pd_before.jpg}
\caption[SEM images of W powder before growth]{SEM images of W powder before growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
\label{fig:pdbefore}
\end{figure}
Tungsten metals crystallize in body center cubic (BCC) phase. Overall, we can still discern the facets. The 4N5 and 5N powders share similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d). In contrast, 3N powders are almost half the size of 3N5 ones, and have more uniform size distribution as well. Absolute size and its distribution play a key role in its usage as seed, which we will talk more in Section~\ref{sec:sgfg}.
% powder after growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{pd_after.jpg}
\caption[SEM images of W powder after growth]{SEM images of W powder after growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
\label{fig:pdafter}
\end{figure}
After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both develop the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) become bundled rods. This difference mainly arise from the average size.

\textbf{OT growth of 3N}

The sodium contents in 3N powders fundamentally change the deposition in OT growth. Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate was shown in Fig.~\ref{fig:nawoxsemedx}a. The nanostructures are NWs with lengths from tens microns up to several hundred microns and diameters about 40 to 500 nm. The deposition of nanowires was generally located on the substrates with a growth temperature range from 660 to 420 \si{\degreeCelsius}. Close-up observations at high magnification revealed some nanowires were cylinder-shaped and some were belt-shaped. At some locations, microplate structures with a regular rectangular shape grew among the nanowires as demonstrated in Fig.~\ref{fig:nawoxsemedx}b and its inset. The chemical compositions of the deposition were identified by EDX. A representative EDX spectrum in Fig.~\ref{fig:nawoxsemedx}c shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate. The crystal structures of the as-synthesized specimens were examined using XRD. The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}d. The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase\footnote{ICDD PDF 04-012-4449,\emph{a}=7.2740\AA, \emph{b}=7.2911\AA, \emph{c}=18.5510\AA, $\alpha$=96.3750$^\circ$, $\beta$=90.8920$^\circ$, $\gamma$=119.6560$^\circ$} and the triclinic \ce{Na2W4O_{13}} phase.\footnote{ICDD PDF 04-012-7108,\emph{a}=11.1630\AA, \emph{b}=3.8940\AA, \emph{c}=8.2550\AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$} The tungsten oxide is the monoclinic \ce{WO3} phase.\footnote{ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA, $\beta$=90.8920$^\circ$}

@@

The XRD measurements revealed the overall structure of the depositions on the substrates. To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and EDX were performed on more than 20 nanowires. The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase. (Fig.~\ref{fig:nawoxtem}a-c) The HRTEM image in Fig.~\ref{fig:nawoxtem}b reveals that the nanowire has a single-crystalline structure. The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}b was recorded in $[\bar{1}10]$ axis. Based on the analyses on a series of diffraction patterns and HRTEM images, the nanowire was confirmed as the triclinic \ce{Na5W_{14}O_{44}}. The growth direction of \ce{Na5W_{14}O_{44}} NWs was determined to be parallel to the (001) plane. The chemical composition of the nanowire was revealed by EDX. Fig.~\ref{fig:nawoxtem}c shows the nanowire consisted of W, Na, and O. No other impurities were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder. They are not compositions from the nanowires and other structures studied here.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase. (Fig.~\ref{fig:nawoxtem}d-f) The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}e was recorded in [100] zone. The growth direction of the \ce{WO3} nanowire was determined to be perpendicular to the (002) plane with a d-spacing of 0.38 nm. EDX spectrum in Fig.~\ref{fig:nawoxtem}f shows the nanowire consisted of W and O without Na or other impurities. The rectangular microplate structures shown in Fig.~\ref{fig:nawoxsemedx}b were also collected for TEM examination. These microplate structures were identified to be the triclinic \ce{Na2W4O_{13}} phase. The SAED in Fig.~\ref{fig:nawoxtem}h was recorded in [101] axis. No high-quality HRTEM images were acquired for the \ce{Na2W4O_{13}} plate due to its thickness. The long edge of the plate was identified as parallel to the (010) plane and the short edge parallel to the ($\bar{1}01$) plane. From XRD spectra, the long edge of \ce{Na2W4O_{13}} plate can be figured out as the $\vec{c}$ axis ([001]) and the short edge is along the $\vec{b}$ axis ([010]). Fig.~\ref{fig:nawoxtem}i shows the plate structure also consisted of W, Na, and O and no other impurities were detected. Normalized to the highest W peak, the Na peak intensity in Fig.~\ref{fig:nawoxtem}i is higher than the one in Fig.~\ref{fig:nawoxtem}c. This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than the one for \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of the two phases.

@@

Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires. Fig.~\ref{fig:nawoxram}a shows the mRaman spectrum of the microplates. The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matches the reported \ce{Na2W4O_{13}} Raman shift frequencies. \cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires is shown in Fig.~\ref{fig:nawoxram}b. The spectrum shows major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions. As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consist of only little or no amount of \ce{WO3} and \ce{Na2W4O_{13}} phases. Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be fitted. According to the TEM results, the nanowires are mainly \ce{Na5W_{14}O_{44}}, therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase. Sofar no Raman spectrum has been reported this phase, hence we are probably the first to observe the Raman spectrum for \ce{Na5W_{14}O_{44}}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_raman_series}
\caption[Raman spectra on \ce{Na_xWO3}]{Micro-Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
\label{fig:nawoxram}
\end{figure}

Heated at elevated temperatures, the W source, quartz tube, and quartz boat were the three possible sources for Na. The sodium concentration in 3N source was 20ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm,  respectively. To confirm the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N). These ultra-high purity W sources produced pure tungsten oxide deposition.  No Na content was detected. These results verified the Na content was mainly from the 3N W powders, not from the quartz tube and boat. In the experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other substoichiometric tungsten oxide vapors. The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by (i) only small amount of the tungsten source was consumed during the growth and (ii) only the top layer of the tungsten source was oxidized with a dark blue color. Due to its low concentration, the exact composition of the Na content in the tungsten source is not clear. However, the evaporation rate of the Na content is expected to be high as heated at 1000 \si{\degreeCelsius}. This assumption is supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source. Put it in another way, this means that the majority of Na content was already evaporated in previous experiment. Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth was comparable to or more than the amount of tungsten oxide vapors and resulted in the dominating deposition of sodium tungsten oxide phases in the nanowire growth region.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{nawox_edx_series.jpg}
\caption[Photograph of a series of 3N growth]{(a) Photograph of a series of specimens grown in the same reaction chamber with the increase of growth number showing different growth zones and corresponding morphology changes. (b) Change of Na/W ratios with the increase of growth number at different growth zones.}
\label{fig:nawoxser}
\end{figure}

As shown by the photograph in Fig.~\ref{fig:nawoxser}a, for a series of growth performed in the same reaction chamber, the morphology of the nanowires changes with the increase of growth numbers. Three growth zones of nanowires can be identified in basis of the coverage and density of the nanowires, as delimited by the vertical guide line. The growth Zone I was located at high temperature end ranging from 660 to 520 \si{\degreeCelsius}, Zone II was from 520 to 470 \si{\degreeCelsius}, and Zone III from 470 to 420 \si{\degreeCelsius}. Detailed morphological changes are depicted in Fig.~\ref{fig:nawoxsemall}.

@@

For the first growth (Fig.~\ref{fig:nawoxsemall}a-c) in a new clean reaction chamber, there were only a little nanowires scattered in Zone I (Fig.~\ref{fig:nawoxsemall}a), ultra-long nanowires were mostly found in Zone II with higher density and coverage (Fig.~\ref{fig:nawoxsemall}b), and in Zone III the coverage, density, and length of nanowires gradually reduced as the growth location moved downstream (Fig.~\ref{fig:nawoxsemall}c). With growth number increased to the third growth (Fig.~\ref{fig:nawoxsemall}d-f) and to the fifth growth (Fig.~\ref{fig:nawoxsemall}g-i), the coverage, density, and length of the nanowires increased in all three zones. Zone I had the most significant morphology changes as shown by Fig.~\ref{fig:nawoxser}a and Fig.~\ref{fig:nawoxsemall}g. After fifth growth in the same reaction chamber, the deposition of ultra-long nanowires almost covered all three zones. For Zones I and II, no significant morphology change was observed with further increase of the growth number up to 8th growth. However, for Zone III the microplate structures (shown in inset of Fig.~\ref{fig:nawoxsemall}i) kept increasing significantly with the growth number. EDX study revealed the change of Na concentration in the deposition with the growth number. Fig.~\ref{fig:nawoxser}b shows the variation of the Na/W ratios with the increase of growth number at different nanowire growth zones. Generally, the Na/W ratios at all growth zones increased with the increase of growth number. The large fluctuation of Na/W ratio at Zone III was mainly due to the uneven distribution of Na content with different morphologies at Zone III.

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{nawox_sch.jpg}
\caption[Schematic drawings of residual \ce{Na_xWO3} growth]{Schematic drawings showing (a) growth with tungsten source in a new tube, (b) enhanced growth with both residue deposition and tungsten source, and (c) growth with residue deposition only.}
\label{fig:nawoxsch}
\end{figure}

A mechanism of residue deposition enhanced growth was proposed to explain the morphology change of the nanowires with the growth number. Since the CVD setup employed here is a hot-wall CVD system, deposition formed on the substrate surface as well as on the inner wall of the reaction chamber in the growth area. Residue deposition was fund on the quartz tube which can be distinguished by the color change on the quartz tube after each growth. With the increase of growth number for the same reaction chamber, the residue deposition on the inner wall of the tube also increased. If a clean quartz tube free of any residue deposition is used as the reaction chamber, the vapors are supplied only from the source material forming deposition in the growth area with lower temperature (as shown by the schematics in Fig.~\ref{fig:nawoxsch}a). When a quartz tube with residue deposition from previous depositions is used repeatedly as the reaction chamber, the residue deposition heated at growth temperature will also produce vapor locally. Therefore, the vapors from both the source materials and the local residue deposition will result in an enhanced growth of nanowires (Fig.~\ref{fig:nawoxsch}b). To prove this hypothesis, control experiments were performed utilizing a quartz tube used multiple times previously (e.g., a growth number of 9). The experiments were carried out without any source materials while other growth parameters remain unchanged. Similar nanowires were found on the substrate in the nanowire growth zones. Without the source materials, the residue deposition from the tube surface was the only possible source that could produce vapors forming nanowires on the substrate (Fig.~\ref{fig:nawoxsch}c). This result confirmed the nanowire growth could be enhanced by the presence of the residue deposition and explained the morphology changes of the nanowires with the increase of growth number.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{wox_xrd_series}
\caption[XRD spectra evolution of \ce{Na_xWO3} growth]{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
\label{fig:nawoxxrd}
\end{figure}

The general trend of Na/W ratios with the growth number can also be explained by the aforementioned effect of residue deposition. The sodium contents from the residue deposition will join the new Na contents from the W source forming deposition. Fig.~\ref{fig:nawoxxrd} shows the XRD spectra of a series of specimens with the growth number increases from 1 to 5. The XRD spectra also reveal the revolution of the three phases with changes of relative concentrations as the growth number increases. Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increase significantly as the growth number increase from 1 to 5. And in the 5th growth, \ce{Na2W4O_{13}} become the dominated phase compared to the other two phases. These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDS measurements (Fig.~\ref{fig:nawoxser}b).

\textbf{OT growth of 3N5, 4N5 and 5N}

Typical morphologies of OT growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively. The common feature is the deposition is dominated by islands in upstream end and layers in downstream end. The exact dimension still shows some minor difference, particularly in low temperature region. The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder. 
% 3N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
\label{fig:wox3n5}
\end{figure}
It is worth pointing out that we found some NWs growth in low temperature end associated with 4N5 (Fig.~\ref{fig:wox4n5}c), although the density is not large. We managed to enhance the coverage as discussed in Section~\ref{sec:sgfg}.
% 4N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox4n5.jpg}
\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature. Growth with 5N powders have almost the same morphology with that of 4N5, and is not shown in this work}
\label{fig:wox4n5}
\end{figure}

@@

Commercial available tungsten powders with different size are usually associated with purity variation as well. We investigated four kinds of tungsten powder as already summarized in Table~\ref{tab:powder}. The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs. We performed a systematic investigation on the oxidation behavior of tungsten powder. In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 5--8 mTorr. Then oxygen flow varying between 1 sccm to 10 sccm was admitted from upstream inlet. With 10 sccm Ar as carrier gas, the overall pressure was about 100 mTorr. The heating temperature was in the range of 500 to 750 \si{\degreeCelsius}. We present the temperature effect, size-dependence and influence of oxygen partial pressure as following.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig1.jpg}
\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500\si{\degreeCelsius}, b) 600\si{\degreeCelsius}, c) 650\si{\degreeCelsius}, d) 750\si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650\si{\degreeCelsius}. Oxygen flow rate is 1 sccm.}
\label{fig:pdtemp}
\end{figure}

Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder. At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow. When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface. Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures. It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig3.jpg}
\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow. a) $17\mu m$, b) $32\mu m$, c) $3.3\mu m$, d) $1.5\mu m$.}
\label{fig:pdsize}
\end{figure}

Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions. In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature. This dramatic difference could be explained in terms of surface energy and oxygen diffusion. With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder. When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition. Since the size distribution of 3N powder is more uniform than that of 3N5 powder, we only employed the former as seeds.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig2.jpg}
\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm. The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
\label{fig:pdoxy}
\end{figure}

@@

%FG
As shown in Fig.~\ref{fig:wogrowsf}b, we use two substrates in flow growth, each of which is approximate 12mm long. Substrate 1 (Sub1) is located at 6.75 to 7 inch (See Fig.~\ref{fig:wogrow} horizontal axis), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1. Source (4N5 and 5N powder) is located at 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure. Deposition on sub1 is characterized by dense layer, similar to those shown in Fig.~\ref{fig:wox4n5}b. However, deposition on sub2 (Fig.~\ref{fig:sg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber. The NW density is dramatically increased in flow growth layout. The NWs have length about 1 to 2 $\mu m$ and diameter about 200 nm. Close-up view (inset of Fig.~\ref{fig:sg2}) show the NWs have clear facets, implying its high crystalline quality.
% fg sem
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:sg1}\includegraphics[width=0.45\textwidth]{wox_flow1}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:sg2}\includegraphics[width=0.45\textwidth]{wox_flow2}}
\caption[Characterization of flow growth \ce{WO3}: SEM]{ (a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
\label{fig:fgsem}
\end{figure}
TEM to be done on D8. 
% fg tem 
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.8\textwidth]{wo3_tem.jpg}
%\caption[Flow growth of \ce{wo3}:TEM]{TEM characterization of FG \ce{WO3} NWs. }
%\label{fig:fgtem}
%\end{figure}

The growth mechanism stay the same as aforementioned VS process. Both local flow and temperature play an vital role in the formation of dense NW array. Splitting one substrate into two presumably introduces some fluctuation in the vapor flow. It is well known that in lamellar flow region, there is a velocity boundary above the side wall.
